---
title: "hw5"
author: "Ty Darnell"
date: "October 10, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = F,message=F)
library(tidyverse)
library(knitr)
pgedat=read_table2("HW2_PGE.txt",col_names=c("patient", "ipge", "ca", "hypercalcemia"))
pgedat$hypercalcemia=as.factor(pgedat$hypercalcemia)
```

#Problem 1

$F_1$ = group of subjects without hypercalcemia

$F_2$ = group of subjects with hypercalcemia

$F_1(y)$ = distribution of `ipge` for group of subjects without hypercalcemia

$F_2(y)$ = distribution of `ipge` for group of subjects with hypercalcemia

$H_0:F_1(y)=F_2(y)$ for all y

$H_A: F_1(y)\neq F_2(y)$ for at least one y

$D=\max_y|F_{1n}(y)-F_{2m}(y)|$

$F_{1n}(y)$= Emperical Distribution Function for the sample from $F_1$

$F_{2m}(y)$= Emperical Distribution Function for the sample from $F_2$

```{r}
hca2=pgedat%>%filter(hypercalcemia==1)

hca1= pgedat%>%filter(hypercalcemia==0)

f1=hca1$ipge

f2=hca2$ipge

 ks.test(f1,f2)

```

Using $\alpha = .05$

D=.62727

pvalue =.03242

since $pvalue<.05$ reject $H_0$

We conclude that the distributions of `ipge` may be different for people with and without hypercalcemia.

#Problem 2

```{r}
fisher.test(matrix(c(21,2,2,8),nrow=2),alternative="greater")

```

$\alpha=.05$

$pvalue=.0001255$

Reject $H_0$ since $pvalue<.05$
